Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
pushed new examples section

\ssec{Genus One Base Cases}
\label{ssec:g_1_base}

We first analyze the following two examples, which will be crucial base cases for our inductive approach, completed in Subsection ~\ref{ssec:main_g_1}.

@@

%The base case of $L' = \frac{3}{7}P_1$ has $R_L \cong k[u, y_5, y_7]/(y_5)^3 - uy_7^2.$

The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed. Note that just like $L' = P - Q + \frac{2}{5}P_1$ is an exceptional case, as noted at the end of Example ~\ref{eg:exception-1-5}, $L' = \frac{3}{7}P_1$ is yet another exceptional case.

@@

Before proving Lemma ~\ref{lem:g-0-admissible-cases} in general, we check the lemma holds for case (b).

>>>>

\ssec{Genus One Base Cases}
\label{ssec:g_1_base}
In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g=1$.

@@

The cases that $L' = 0, \: L' = P-Q +\frac{1}{3}P_1 + \frac{1}{3}P_2,$ and $L' = P-Q + \frac{2}{5}P_1$ were checked in Examples ~\ref{eg:base-1-0}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} respectively.

The base cases of $L' = \frac{3}{7}P_1$ and $L' = \frac{1}{3}P_1 +\frac{1}{3}P_2$ can be similarly computed. Note that in addition to $L' = P - Q + \frac{2}{5}P_1,$ and $L' = \frac{3}{7}P_1$ being base cases, they are also exceptional cases, as listed in Table ~\ref{table:g-1-exceptional}.

@@

Note that Example ~\ref{eg:base-377}, precisely proves case (b) of Lemma ~\ref{lem:g-0-admissible-cases}.
